---
title: "NRG-GY003 TCR Analysis"
subtitle: "TCR analysis of NRG-GY003 ovarian cancer tumors and peripheral blood"
description: "Analysis of bulk TCR-seq (DNA) from archival tissue samples and pre- and post-treatment peripheral blood samples from patients with recurrent ovarian cancer treated with immune checkpoint inhibitors (NIVO or IPI/NIVO) treated on the NRG-GY003 clinical trial."

author:
  - name: Kelsey Monson
    degrees:
      - PhD
      - MS
    orcid: 0000-0003-1093-8628
    email: kelsey.monson@mssm.edu
    affiliations:
      - ref: ISMMS

affiliations:
  - id: ISMMS
    name: Icahn School of Medicine at Mount Sinai
    city: New York
    state: NY
    department: Immunology and Immunotherapy

title-block-banner: "#f0f3f5"
title-block-banner-color: "black"

keywords: "Genomics, TCR, Immunotherapy, R, Ovarian Cancer"
date: today

format: 
  html: 
    toc: true
    code-overflow: wrap
    embed-resources: true
    
fig-cap-location: margin
execute:
 warning: false
editor: visual
---

# Introduction

I have used MiXCR to define CDR3 sequences from Cellecta sequencing of bulk tumor and blood TCRs from the NRG-GY003 clinical trial.

*Add demographic table here of samples with TCR-seq*

## Cellecta and MiXCR

*Add more details on the sequencing and MiXCR here*

# Immunarch Analysis

```{r}
#| code-fold: true

# Package for immune repertoire analysis 
library(immunarch)

## Load the other packages up here
```

The `immunarch` plots are not well-designed for the number of samples we have, so I've broken up the analysis by treatment (Nivo and Combo) and response (Clinical Benefit and No Clinical Benefit)

## TRB

I started by first analyzing the TRB data (based in part on [this](https://www.nature.com/articles/s41591-019-0734-6) study that showed the strongest signal with TRB chains).

**Nivo Clinical Benefit**

```{r}
# Load the data
immdata.nivoCB <- repLoad("input/TRB/Nivo_CB/")


# Calculate and visualise basic statistics ----
repExplore(immdata.nivoCB$data, "volume") %>% vis() # Number of unique clonotypes
repExplore(immdata.nivoCB$data, "volume") %>% vis(.by="Tissue_Type",.meta=immdata.nivoCB$meta) # Number of unique clonotypes by tissue type (normal/tumor)
# Unsurprisingly, the tumor samples have far fewer unique clones than the blood

repExplore(immdata.nivoCB$data, "volume") %>% vis(.by="Tissue_Timepoint",.meta=immdata.nivoCB$meta)
# Slight trend towards fewere unique clones at later treatment timepoints, potentially indicative of ICI-induced clonal expansion, but no statistical difference


repExplore(immdata.nivoCB$data, "clones") %>% vis() # Number of clones (i.e., cells) per input repertoire
repExplore(immdata.nivoCB$data, "clones") %>% vis(.by="Tissue_Type",.meta=immdata.nivoCB$meta) # Number of clones per input repertoire by tissue type

# So the absolute number of clones (or T cells) in tumor is much higher, but the repertoire diversity is lower


repClonality(immdata.nivoCB$data, "homeo") %>%  vis() # Visualise the relative abundance of clonotypes
repClonality(immdata.nivoCB$data, "homeo") %>%  vis(.by="Tissue_Type",.meta=immdata.nivoCB$meta) # Visualise the relative abundance of clonotypes by tissue type
repClonality(immdata.nivoCB$data, "homeo") %>%  vis(.by="Tissue_Timepoint",.meta=immdata.nivoCB$meta) # Visualise the relative abundance of clonotypes by tissue and timepiont

#Provides a bit more evidence of treatment-induced clonal expansion, but not statistically different
```
